\begingroup 
\renewcommand{\section}[2]{\anonsection{Список использованных источников}}
\begin{thebibliography}{99}

\bibitem{urevich}
	Е.И.Юревич  
    <<Основы робототехники>>,
    БХВ-Петербург,  
    -- 304 с. 2017.

\bibitem{evolution}
	L.Silva, A.Silva
	<<An Evolutionary Algorithm for Autonomous Robot Navigation>>,
	The International Conference on Computational Science,
	2016.

\bibitem{fuzzy}
	Л.Заде 
	<<Понятие лингвистической переменной и его применение к принятию приближенных решений>>,
	М.: Мир,  
	-- 166 с. 1976.

\bibitem{fuzzy1}
	М.С.Ситников
	<<Анализ и синтез интеллектуальных систем автоматического управления с нечеткими регуляторами>>,
	Москва,
	2008.

\bibitem{fuzzy2}
	A.Eid, R.Abdel-Fadil
	<<Fuzzy logic control of modern aircraft actuators>>,
	3rd International Conference on Energy Systems and Technologies,
	2015.

\bibitem{fuzzy3}
	P.Lamkhade, C.B.Kadu
	<<Design and implementation of fuzzy logic controller for level control>>,
	3rd International Conference on Energy Systems and Technologies,
	2015.

\bibitem{reinf_lern}
	Обучение с подкреплением,
	[Электронный ресурс]. --
	URL: http://apsheronsk.bozo.ru/Neural/Lec8.htm
	(Дата обращения: 12.01.2019).

\bibitem{reinf_lern1}
	I.Zamora, N.G.Lopez
	<<Extending the OpenAI Gym for robotics: a toolkit for reinforcement learning using ROS and Gazebo>>,
	arXiv:1608.05742v2,
	2016.

\bibitem{reinf_lern2}
	E.Tzeng, C.Devin
	<<Adapting Deep Visuomotor Representations with Weak Pairwise Constraints>>,
	arXiv:1511.07111v5,
	2015.

\bibitem{reinf_lern3}
	C.Florensa, D.Held
	<<Automatic Goal Generation for Reinforcement Learning Agents>>,
	arXiv:1705.06366,
	2018.

\bibitem{CEM}
	D.P.Kroese
	<<Cross-Entropy Method>>,
	arXiv:1503.01842v1,
	2015.

\bibitem{CEM1}
	S.T.Tokdar, R.E.Kass
	<<Importance Sampling: A Review>>,
	Department of Statistics, Carnegie Mellon University, Pittsburgh, 
	2008.
	
\bibitem{DUEL_DQN}
	V. Mnih
	<<Human-Level Control through Deep Reinforcement Learning>>,
	journal Nature, 
	2015.

\bibitem{Nikolenko}
	C.И.Николенко  
	<<Глубокое обучение. Погружение в мир нейронных сетей>>,
	Питер,  
	-- 480 с. 2018.


\bibitem{pgms}
	Policy gradient methods,
	[Электронный ресурс]. --
	URL: https://medium.freecodecamp.org/an-introduction-to-policy-gradients-with-cartpole-and-doom-495b5ef2207f
	(Дата обращения: 15.01.2019).

\bibitem{ddpg}
	T.P.Lillicrap, J.J.Hunt
	<<Continuous control with deep reinforcement learning>>,
	arXiv:1509.02971, 
	2015.

\bibitem{trpo}
	J.Schulman, S.Levine
	<<Trust Region Policy Optimization>>,
	arXiv:1502.05477v5, 
	2017.

\bibitem{trpo1}
	P.Bansal, E.Guerra
	<<Minorization-Maximization (MM) algorithms for semiparametric logit models: Bottlenecks, extensions, and comparisons>>,
	School of Civil and Environmental Engineering, Cornell University, USA, 
	2018.
	
\bibitem{ppo}
	J.Schulman, F.Wolski, P.Dhariwal, A.Radford, O.Klimov
	<<Proximal Policy Optimization Algorithms>>,
	arXiv:1707.06347v2, 
	2017.

\bibitem{mujoco}
	MuJoCo -- documentation,
	[Электронный ресурс]. --
	URL: http://www.mujoco.org/book/index.html
	(Дата обращения: 12.01.2019).

\end{thebibliography}
\endgroup

\clearpage
